Compressive Channel Sensing of Multipath Millimeter Channel via a Beamspace Dantzig Selector and its Probabilitic Performance Bound

### 2019-01-08 ongoing/report/sec_3_theorems_and_proofs.tex
Create slides

We first establish a technical lemma that shows \(\RM{supp}(g)\) has roughly cardinal \(s\).
At the heart of the argument, the lemma provides the basis on which \(g\) is almost-sparse.

@@

\Result
{Definition}
{
For \(x \in \MB{V}_{\MB{K}}(N)\), we say \(x\) is almost-\(s\)-sparse with \(\ell_1\)-residue \(R\), where \(s \ll N\), if
\Disp{
\sum_{n=s+1}^N |S(x) (n)|
\leq R.
}
}

@@

Particularly, for arbitrary \(\f\), find \(k\) so that
\Disp{
\eta :=&\f -\F{2\pi k}{N_H}, \\
\left| \eta \right|
\leq &\F{2\pi}{N_H}.
}
%
Then observe
\Disp{
K^\H a(\f) (k)
=\F{1}{N_H} D \left( \f -\F{2 \pi k} {N_H} \right)
}
So we need only bound
\Disp{
R(\eta)
:=\F{1}{N_H} \sum_{n_H =s}^{N_H -1} D \left( \eta +\F{2 \pi n_H} {N_H} \right)
}
By the approximation of rectangle to integral,
\Disp{
R(\eta) -\F{2\pi} {N_H}
\leq \F{1}{N_H} N_H \int_{\f'=2\pi L/N_H}^{2\pi} |D(\f')| d \f'
}
Bound \(D\) by above technique, meanwhile we notice \(\f' <24\).
\Disp{
R(\f)
\leq &\F{1}{2\pi} \int_{\f'=2\pi L/N_H}^{2\pi} \F{48}{(24 -\f'^2) \f'} d \f'
+\F{2\pi} {N_H} \\
=&\F{1}{\pi} \log \F{2\pi N_H}{L}
-\F{1}{N_H} \log \F{4\pi^2 -24} {L^2/N_H^2 -24}
+\F{2\pi} {N_H}
}
Notice the argument of log in the second term \(<1\), and we drop that.
Also drop \(2\pi /N_H\) since it is small.
Furthermore the \(2\pi\) factor in log can be dropped too.
\Disp{
R(\f)
\leq \F{1}{\pi} \log \F{N_H}{L}.
}

\Result
{Lemma (Tentative)}
{
Let \(\f\) and \(\th\) be uniformly, independently distributed in \([0,2\pi)\), and linear array response \(\V{a}\) defined as in ().
Let \(g\) be defined as above.
Then \(g\) is almost-\(L\)-sparse with \(\ell_1\)-residue \(R(N_H, L)\) to be
%
\Disp{
R
\leq \F{L}{\pi^2} \left( \log \F{N_H}{L} \right)^2
}
}

@@

\Result
{Definition}
{
For \(\MC{T}, \MC{T}' \subset \{1, \dotsc, N_p\}\), define the \(s,s'\)-restricted orthogonality constant \(\tau_{s,s'} >0\) to be the smallest such that
%
\Disp{
| \IP{ P_{\MC{T}} h, P_{\MC{T}'} h' } |
\leq \tau_{s, s'} \cdot \| h \|_2 \|h'\|_2
}
}

@@

\Result
{Proposition}
{
Let \(g\) and \(d\) be defined as above.
Then
%
\Disp{
\|d_{\MC{C}}\|_1
\leq \|d_{\MC{A}}\|_1 +2\|g_{C}\|_1
}
}

To show this, observe that with triangle inequality applied respectively on \(\MC{A}\) and \(\MC{C}\),
\Disp{
\|g\|_1
-\|d_{\MC{A}}\|_1
+\|d_{\MC{C}}\|_1
-\|g_{\MC{C}}\|_1
\leq \|g+d\|_1
}
In the first line, we recall \(g =g_{\MC{A}}\).
On the other hand, by construction that \(\hat{g}\) minimizes the \(\ell_1\)-norm,
\Disp{
\|g+d\|_1
=\|\hat{g}\|_1
\leq \|g\|_1
}
The result follows by combining.

\Result
{Lemma}
{
Let \(z\) and \(P\) be defined as above.
Then
%
\Disp{
|\IP{ z, P(:, n_g) }|
\leq& 2 \R{\log N_g},
\quad n_g =1, \dotsc, N_g.
}
%
with overwhelming probability.
}

This only depends on the fact that \(P(:, n_g)\) has unity \(\ell_2\)-norm, and on the randomness of \(z\).

@@

\Result
{Lemma}
{
Let \(d\) and \(P\) be defined as above, and \(P\) satisfies RIP as in ().
%
\Disp{
\|P^\H P d\|_\infty
\leq& 4 \R{\log N_g},
\quad n_g =1, \dotsc, N_g.
}
}

To show this, by definition
%
\Disp{
&\IP{ z -(y -P \hat{g}), P (:,n_y) } \NT \\
=&\IP{ P \hat{g} -P g, P (:,n_y) } \NT \\
=&\IP{ P d, P (:,n_y) }
}

By construction
\Disp{
\| P (:,n_y)^\H (y -P \hat{g}) \|
\leq &\| P^\H (y -P \hat{g}) \|_\infty \\
\leq &2\R{\log N_g}
}
By triangle inequality, together with lemma (), we have
\Disp{
\|P (:,n_y)^\H P d\|
\leq &\|\IP{ z, P (:,n_y) }\| +\IP{ y -P \hat{g}, P (:,n_y) } \\
\leq &2 \R{\log N_g} +2 \R{\log N_g}
}
which implies
\Disp{
\|P^\H P d\|_\infty
\leq &4 \R{\log N_g}.
}

@@

\Result
{Lemma}
{
Let \(d\) and \(P\) be defined as above, and \(P\) satisfies RIP as in () with respect to \(\d_s\).
%
\Disp{
\|d_{\MC{AB}}\|_2
\leq \F{1}{1-\d_{2L}} \|P_{\MC{A}\MC{B}}^\Tr P d\|_2 +\F{\d_{3L}}{(1-\d_{2L}) \R{L}} \|d_{C}\|_1
}
%
}

@@

\Result
{Lemma}
{
Let \(d\) be defined as above.
Then
%
\Disp{
\|d\|_2^2
\leq \|d_{\MC{A}\MC{B}}\|_2^2 +\F{1}{L} \|d_{\MC{C}}\|_1^2
}
%
}

@@

We can now formulate and prove the main bound of ours.

\Result
{Theorem}
{
Let \(y\), \(P\), \(g\), \(\hat{g}\), \(d\) be defined as above.
Then
\Disp{
\|d\|_2
\leq \F{4 L^4}{\pi^4} \d_{3L}^4 (1-2\d_{2L}) ( \log N_H )^4
}
with overwhelming probability.
}

We are ready to combine previous lemmata.
The first quantity we want to bound away is
\Disp{
\|P_{\MC{A}\MC{B}}^\Tr P d\|_2
\leq &\|P^\Tr P d\|_2 \NT \\
\leq &\R{N_g} \|P^\Tr P d\|_\infty \NT \\
\leq &4 \R{ N_g \log N_g }
}
Thus, by virtue of Lemma (),
\Disp{
\| d_{A} \|_1
\leq &\R{L} \| d_{A} \|_2 \NT \\
\leq &\R{L} \| d_{\MC{AB}} \|_2 \NT \\
\leq &\F {\d_{3L}} {1-\d_{2L}} \| d_{\MC{C}} \|_1 +\F {4} {1-\d_{2L}} \R{L N_g \log N_g} 
}

As the next step, we must eliminate \(\|d_{\MC{A}}\|_1\) in rhs of Lemma ().
\Disp{
\| d_{\MC{C}} \|_1
\leq &\| d_{\MC{A}} \|_1 +2 \| g_{\MC{C}} \|_1 \NT \\
\leq &\F {\d_{3L}} {1-\d_{2L}} \| d_{\MC{C}} \|_1
+2 \| g_{\MC{C}} \|_1
+\F {4} {1-\d_{2L}} \R{L N_g \log N_g}
}
Or,
\Disp{
\| d_{\MC{C}} \|_1
\leq &2 \F{1-\d_{2L}} {1 -\d_{2L} -\d_{3L}} \| g_{\MC{C}} \|_1
+\F {4} {1-\d_{2L} -\d_{3L}} \R{L N_g \log N_g}
}

We are ready to bound \(\| d \|_2^2\).
Using Lemma () again, we have
\Disp{
\| d \|_2^2
\leq &\|d_{\MC{A}\MC{B}}\|_2^2 +\F{1}{L} \|d_{\MC{C}}\|_1^2 \NT \\
\leq & \left( \F{\d_{3L}^2} {L^2 (1-\d_{2L})^2} +\F{1}{L} \right) \|d_{\MC{C}}\|_1^2
+\F{8 \d_{3L}} {L (1-\d_{2L})^2} \R{N_g \log N_g} \|d_{\MC{C}}\|_1 \NT \\
&\quad +\F{16}{(1-\d_{2L})^2} N_g \log N_g
}
Finally, plug in the bound for \(\|d_{\MC{C}}\|_1\), the last unknown, and we make use of the almost-sparsity condition of \(\|d_{\MC{C}}\|_1\).
There are several dozens of terms if we expand all.
but for simplicity, we keep only the leading term under the approximation
\Disp{
1 \ll L \ll N_g
}
And expand to the first order expressions containing \(\d_{2L}\) or \(\d_{3L}\) in the denominator using
\Disp{
\d_{2L} <\d_{3L} \ll 1.
}
Then
\Disp{
\|d\|_2^2
\leq \F{4 L^4}{\pi^4} \d_{3L}^4 (1-2\d_{2L}) ( \log N_H )^4
}

>>>>

We first establish a technical lemma that shows \(\RM{supp}(g)\) has roughly cardinal \(L\), which guarantees, at the heart of the argument, that \(g\) is almost-sparse

@@

\Result
{Definition}
{
For \(\V{x} \in \MB{V}_{\MB{K}}(N)\), we say \(\V{x}\) is almost-\(s\)-sparse with \(\ell_1\)-residue \(R\), where \(s \ll N\), if
\Disp{
\sum_{n=s+1}^N |S(\V{x}) (n)|
\leq R.
}
}

@@

Particularly, for arbitrary \(\f\), find \(k\) so that
\Disp{
\eta :=&\f -\F{2\pi k}{N_H}, \\
\left| \eta \right|
\leq &\F{2\pi}{N_H}.
}
%
Then observe
\Disp{
\M{K}^\H \V{a}(\f) (k)
=\F{1}{N_H} D \left( \f -\F{2 \pi k} {N_H} \right)
}
So we need only bound
\Disp{
R(\eta)
:=\F{1}{N_H} \sum_{n_H =s}^{N_H -1} D \left( \eta +\F{2 \pi n_H} {N_H} \right)
}
By the approximation of rectangle to integral,
\Disp{
R(\eta) -\F{2\pi} {N_H}
\leq \F{1}{N_H} N_H \int_{\f'=2\pi L/N_H}^{2\pi} |D(\f')| d \f'
}
Bound \(D\) by above technique, meanwhile we notice \(\f' <24\).
\Disp{
R(\f)
\leq &\F{1}{2\pi} \int_{\f'=2\pi L/N_H}^{2\pi} \F{48}{(24 -\f'^2) \f'} d \f'
+\F{2\pi} {N_H} \NT \\
=&\F{1}{\pi} \log \F{2\pi N_H}{L}
-\F{1}{N_H} \log \F{4\pi^2 -24} {L^2/N_H^2 -24}
+\F{2\pi} {N_H}
}
Notice the argument of log in the second term \(<1\), and we drop that.
Also drop \(2\pi /N_H\) since it is small.
Furthermore the \(2\pi\) factor in log can be dropped too.
\Disp{
R(\f)
\leq \F{1}{\pi} \log \F{N_H}{L}.
}

\Result
{Lemma (Tentative)}
{
Let \(\f\) and \(\th\) be uniformly, independently distributed in \([0,2\pi)\), and linear array response \(\V{a}\) defined as in ().
Let \(\V{g}\) be defined as above.
Then \(\V{g}\) is almost-\(L\)-sparse with \(\ell_1\)-residue \(R(N_H, L)\) to be
%
\Disp{
R
\leq \F{L}{\pi^2} \left( \log \F{N_H}{L} \right)^2
}
}

@@

\Result
{Definition}
{
For \(\MC{T}, \MC{T}' \subset \{1, \dotsc, N_p\}\), define the \(s, s'\)-restricted orthogonality constant \(\tau_{s,s'} >0\) to be the smallest such that
%
\Disp{
| \IP{ P_{\MC{T}} h, P_{\MC{T}'} h' } |
\leq \tau_{s, s'} \cdot \| h \|_2 \|h'\|_2
}
}

@@

\Result
{Proposition}
{
Let \(\V{g}\) and \(\V{d}\) be defined as above.
Then
%
\Disp{
\|\V{d}_{\MC{C}}\|_1
\leq \|\V{d}_{\MC{A}}\|_1 +2\|\V{g}_{C}\|_1
}
}

To show this, observe that with triangle inequality applied respectively on \(\MC{A}\) and \(\MC{C}\),
\Disp{
\|\V{g}\|_1
-\|\V{d}_{\MC{A}}\|_1
+\|\V{d}_{\MC{C}}\|_1
-\|\V{g}_{\MC{C}}\|_1
\leq \|\V{g} +\V{d}\|_1
}
In the first line, we recall \(\V{g} =\V{g}_{\MC{A}}\).
On the other hand, by construction that \(\hat{g}\) minimizes the \(\ell_1\)-norm,
\Disp{
\|\V{g} +\V{d}\|_1
=\|\hat{\V{g}}\|_1
\leq \|\V{g}\|_1
}
The result follows by combining.

\Result
{Lemma}
{
Let \(\V{z}\) and \(\M{P}\) be defined as above.
Then
%
\Disp{
|\IP{ \V{z}, \M{P}(:, n_g) }|
\leq& 2 \R{\log N_g},
\quad n_g =1, \dotsc, N_g.
}
%
with overwhelming probability.
}

This only depends on the fact that \(\M{P}(:, n_g)\) has unity \(\ell_2\)-norm, and on the randomness of \(\V{z}\).

Recall the following bound for \(Q\) function
\Disp{
Q(x)
\leq \F{1}{2} \RM{e}^{-x^2/2}
}
Particularly, for \(x =\R{2 \log N_g}\), according to CLT,
\Disp{
Q(\R{2 \log N_g})
=\F{1}{N_g}.
}

@@

\Result
{Lemma}
{
Let \(\V{d}\) and \(\M{P}\) be defined as above, and \(\M{P}\) satisfies RIP as in ().
%
\Disp{
\|\M{P}^\H \M{P} \V{d}\|_\infty
\leq& 4 \R{\log N_g},
\quad n_g =1, \dotsc, N_g.
}
}

To show this, by definition
%
\Disp{
&\IP{ \V{z} -(\V{y} -\M{P} \hat{\V{g}}), \M{P} (:,n_y) } \NT \\
=&\IP{ \M{P} \hat{\V{g}} -\M{P} \V{g}, \M{P} (:,n_y) } \NT \\
=&\IP{ \M{P} \V{d}, \M{P} (:,n_y) }
}

By construction
\Disp{
\| \M{P} (:,n_y)^\H (\V{y} -\M{P} \hat{\V{g}}) \|
\leq &\| \M{P}^\H (\V{y} -\M{P} \hat{\V{g}}) \|_\infty \NT \\
\leq &2\R{\log N_g}
}
By triangle inequality, together with Lemma (), we have
\Disp{
\|\M{P} (:,n_y)^\H \M{P} \V{d}\|
\leq &\|\IP{ \V{z}, \M{P} (:,n_y) }\| +\IP{ \V{y} -\M{P} \hat{\V{g}}, \M{P} (:,n_y) } \NT \\
\leq &2 \R{\log N_g} +2 \R{\log N_g}
}
which implies
\Disp{
\|\M{P}^\H \M{P} \V{d}\|_\infty
\leq &4 \R{\log N_g}.
}

@@

\Result
{Lemma}
{
Let \(\V{d}\) and \(\M{P}\) be defined as above, and \(\M{P}\) satisfies RIP as in () with respect to \(\d_s\).
%
\Disp{
\|\V{d}_{\MC{AB}}\|_2
\leq \F{1}{1-\d_{2s}} \|P_{\MC{A}\MC{B}}^\Tr P d\|_2 +\F{\d_{3s}}{(1-\d_{2s}) \R{s}} \|d_{C}\|_1
}
%
}

@@

\Result
{Lemma}
{
Let \(\V{d}\) be defined as above.
Then
%
\Disp{
\|\V{d}\|_2^2
\leq \|\V{d}_{\MC{A}\MC{B}}\|_2^2 +\F{1}{s} \|\V{d}_{\MC{C}}\|_1^2
}
%
}

@@

We can now formulate and prove the main bound of ours.
Here, we use \(s=L\) as the sparsity threshold.

\Result
{Theorem}
{
Let \(\V{y}\), \(\M{P}\), \(\V{g}\), \(\hat{\V{g}}\), \(\V{d}\) be defined as above.
Then
\Disp{
\|\V{d}\|_2
\leq \F{4}{\pi^4} \d_{3L}^4 (1-2\d_{2L}) L^4 ( \log N_H )^4
}
with overwhelming probability.
}

We are ready to combine previous lemmata.
The first quantity we want to bound away is
\Disp{
\|\M{P}_{\MC{A}\MC{B}}^\Tr \M{P} \V{d}\|_2
\leq &\|\M{P}^\Tr \M{P} \V{d}\|_2 \NT \\
\leq &\R{N_g} \|\M{P}^\Tr \M{P} \V{d}\|_\infty \NT \\
\leq &4 \R{ N_g \log N_g }
}
Thus, by virtue of Lemma (),
\Disp{
\| \V{d}_{A} \|_1
\leq &\R{L} \| \V{d}_{A} \|_2 \NT \\
\leq &\R{L} \| \V{d}_{\MC{AB}} \|_2 \NT \\
\leq &\F {\d_{3L}} {1-\d_{2L}} \| \V{d}_{\MC{C}} \|_1 +\F {4} {1-\d_{2L}} \R{L N_g \log N_g} 
}

As the next step, we must eliminate \(\|d_{\MC{A}}\|_1\) in rhs of Lemma ().
\Disp{
\| \V{d}_{\MC{C}} \|_1
\leq &\| \V{d}_{\MC{A}} \|_1 +2 \| \V{g}_{\MC{C}} \|_1 \NT \\
\leq &\F {\d_{3L}} {1-\d_{2L}} \| \V{d}_{\MC{C}} \|_1
+2 \| \V{g}_{\MC{C}} \|_1
+\F {4} {1-\d_{2L}} \R{L N_g \log N_g}
}
Or,
\Disp{
\| \V{d}_{\MC{C}} \|_1
\leq &2 \F{1-\d_{2L}} {1 -\d_{2L} -\d_{3L}} \| \V{g}_{\MC{C}} \|_1
+\F {4} {1-\d_{2L} -\d_{3L}} \R{L N_g \log N_g}
}

We are ready to bound \(\| d \|_2^2\).
Using Lemma () again, we have
\Disp{
\| \V{d} \|_2^2
\leq &\|\V{d}_{\MC{A}\MC{B}}\|_2^2 +\F{1}{L} \|\V{d}_{\MC{C}}\|_1^2 \NT \\
\leq & \left( \F{\d_{3L}^2} {L^2 (1-\d_{2L})^2} +\F{1}{L} \right) \|\V{d}_{\MC{C}}\|_1^2
+\F{8 \d_{3L}} {L (1-\d_{2L})^2} \R{N_g \log N_g} \|\V{d}_{\MC{C}}\|_1 \NT \\
&\quad +\F{16}{(1-\d_{2L})^2} N_g \log N_g
}
Finally, plug in the bound for \(\|\V{d}_{\MC{C}}\|_1\), the last unknown, and we make use of the almost-sparsity condition of \(\|\V{d}_{\MC{C}}\|_1\).
There are several dozens of terms if we expand all.
but for simplicity, we keep only the leading term under the approximation
\Disp{
1 \ll L \ll N_g
}
And expand to the first order expressions containing \(\d_{2L}\) or \(\d_{3L}\) in the denominator using
\Disp{
\d_{2L} <\d_{3L} \ll 1.
}
Then
\Disp{
\|\V{d}\|_2^2
\leq \F{4}{\pi^4} \d_{3L}^4 (1-2\d_{2L}) L^4 ( \log N_H )^4
}

### 2019-01-08 ongoing/report/sec_5_back_matter.tex
Create slides

This article addresses the problem of effective and estimation of the millimeter wave channel by exploiting its sparsity.
We motivated the problem, and provided a rather broad survey of recent literature.
This article adopts The Dantzig Selector (DS) rather than Orthogonal Matching Pursuit (OMP), like many of past literature, as the estimation algorithm.
Beside exploiting the sparsity of space domain representation as existing literature does, we proceed the estimation algorithm in the spatial frequency domain.
The technique is surely inspiring to future work, as many bounds are ready to be obtained once we change the physical model of the channel.
In addition, we have, as a secondary product, derived the generalization of DS for complex vectors.

>>>>

This article addresses the problem of effective and estimation of the millimeter wave channel by exploiting its sparsity.
We motivated the problem, and provided a rather broad survey of recent literature.
This article adopts The Dantzig Selector (DS) rather than Orthogonal Matching Pursuit (OMP), like many of past literature, as the estimation algorithm.
Rather than exploiting the sparsity of space domain representation as existing literature does, we proceed the estimation algorithm in the spatial frequency domain.
The technique is surely inspiring to future work, as many bounds are ready to be obtained once we change the physical model of the channel.
In addition, we have, as a secondary product, derived the generalization of DS for complex vectors.
